---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# EntwineIndex

<!-- badges: start -->
[![UpdateEntwinePlusIndex](https://github.com/bmcgaughey1/EntwineIndex/actions/workflows/main.yml/badge.svg)](https://github.com/bmcgaughey1/EntwineIndex/actions/workflows/main.yml)
<!-- badges: end -->

EntwineIndex is a simple code repository for code that merges the Entwine lidar data
[index](https://raw.githubusercontent.com/hobu/usgs-lidar/master/boundaries/resources.geojson) created
by Howard Butler ([usgs-lidar](https://github.com/hobu/usgs-lidar)) with the WESM 
index (https://rockyweb.usgs.gov/vdelivery/Datasets/Staged/Elevation/metadata/WESM.gpkg) for the USGS
3DEP data collection. The goal is to add lidar project
information to the Entwine index to facilitate querying the index for data for specific dates.

This code is run daily to maintain synchronization with the Entwine index.

The direct link to the 
[index](https://raw.githubusercontent.com/bmcgaughey1/EntwineIndex/main/Index/ENTWINEBoundaries.gpkg) is:
`https://raw.githubusercontent.com/bmcgaughey1/EntwineIndex/main/Index/ENTWINEBoundaries.gpkg`

When using the index, it may be best to grab a copy of the index and store it locally. However, you 
can read the index directly from GitHub. It is fairly small so the download only takes a few seconds.

The index is used with my [USGSlidar](https://github.com/bmcgaughey1/USGSlidar) R package to help discover
lidar data for specific locations and dates. The index can be accessed in the package using 
fetchUSGSProjectIndex(type = "entwineplus").

```{r eval=FALSE, include=TRUE}
url <- "https://raw.githubusercontent.com/bmcgaughey1/EntwineIndex/main/Index/ENTWINEBoundaries.gpkg"

# use rgdal to read the geopackage
library(sf)

# read directly
projects <- sf::st_read(url, stringsAsFactors = FALSE)

# download to local file using utils library, then read
library(utils)
if (!utils::download.file(url, "ENTWINEBoundaries.gpkg", mode = "wb",)) {
  projects <- sf::st_read("ENTWINEBoundaries.gpkg", stringsAsFactors = FALSE)
}
```
