---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# EntwineIndex

<!-- badges: start -->
<!-- badges: end -->

EntwineIndex is a simple code repository for code that merges the Entwine lidar data index created
by Howard Butler with the WESM index for the USGS 3DEP data collection. The goal is to add lidar project
information to the Entwine index to facilitate querying the index for data for specific dates.

Ultimately, this code will run every night/morning to maintain synchronization with the Entwine index.

This code is very much in development so don't expect much...

```{r cars}

```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

